% Created 2019-01-31 Thu 19:26
% Intended LaTeX compiler: pdflatex
\documentclass[10pt]{article}

\input{structure.tex}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.1 (Org mode 9.1.14)},
 pdflang={English}}
\begin{document}

\parbox[top][0.12\textheight][c]{\linewidth}{ % Parbox to hold the author name and CV text; fixed height to match the coloured box to the right, centred vertically and full line width
    \vspace{-0.08\textheight} % Reduce whitespace above the parbox to separate it from the main content
    \centering % Centre text
    {\LARGE \textbf{Pedro Bruel | Researcher \& Software Engineer}}\\\medskip % Your name
    {\Large Performance Tuning \& Modeling \textbullet{} Optimal Experimental Design}
}

%----------------------------------------------------------------------------------------
%    contact details box
%----------------------------------------------------------------------------------------

\parbox[top][0.12\textheight][c]{\linewidth}{ % Parbox to hold the colour box; fixed height to match the name/CV text to the left, centred vertically and full line width
    \vspace{-0.19\textheight} % Reduce whitespace above the parbox to separate it from the main content
    \centering
    \colorbox{shade}{ % Create the coloured box
        \begin{supertabular}{p{0.75\linewidth}} % Start a table with two columns, the table will ensure everything is aligned
            \raisebox{-1pt}{\faHome} \hspace{0.15cm} 2b Rue Charles Gounod, 38000 Grenoble, France \hspace{0.2cm} \raisebox{-1pt}{\faPhone} \hspace{0.14cm} +33 07 68 33 24 38 \\ % Address
            \raisebox{0pt}{\small\faEnvelope} \hspace{0.2cm} \href{mailto:pedro.bruel@gmail.com}{pedro.bruel@gmail.com} \hspace{0.2cm} \raisebox{0pt}{\small\faDesktop} \hspace{0.2cm} \href{https://www.ime.usp.br/~phrb}{ime.usp.br/\textasciitilde{}phrb} \hspace{0.31cm} \raisebox{-1pt}{\faLinkedin} \hspace{0.2cm} \href{https://www.linkedin.com/in/pedro-bruel}{pedro-bruel} \hspace{0.2cm} \raisebox{-1pt}{\faGithub} \hspace{0.2cm} \href{https://github.com/phrb}{phrb} \\
            % See fontawesome.pdf in the fonts folder for all icons you can use
        \end{supertabular}
    }
}

\vspace{-0.11\textheight} % Reduce whitespace above the parbox to separate it from the main content
\begin{paracol}{2} % Begin the multi-column environment

\section{Experience}
\label{sec:org8187e2a}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\begin{supertabular}{R{0.3\linewidth}L{0.64\linewidth}}

\workposition{2017 -- May 2020}
    {PhD Researcher}
    {Grenoble Informatics Laboratory}
    {University of Grenoble Alpes, France}
    {Developing Design of Experiments Techniques for autotuning High-Performance
    Computing kernels and compilers on CPUs, GPUs and FPGAs}

\workposition{2015 -- May 2020}
    {PhD Researcher}
    {Software Systems Laboratory}
    {University of São Paulo, Brazil}
    {Developed autotuners for High-Level Synthesis compilers for FPGAs and for
    the CUDA Compiler using Search Heuristics}

\workposition{2015 -- 2016}
    {PhD Research Collaborator}
    {Hewllett-Packard Enterprise}
    {University of São Paulo, Brazil}
    {Developed an autotuner for the LegUp High-Level Synthesis compiler for
    Altera FPGAs}

\workposition{2012 -- 2014}
    {Research Intern}
    {Computer Music Research Group}
    {University of São Paulo, Brazil}
    {Maintained and developed a multiagent system for music composition via
    agent interaction}

\end{supertabular}

\vspace{-\baselineskip}\medskip % Standardise the whitespace after this section and before the next (the custom command adds too much otherwise)
\section{Education}
\label{sec:orgc0c1ffd}
\begin{supertabular}{R{0.24\linewidth}L{0.7\linewidth}}
    \workposition{2015 -- 2020}
    {PhD in Computer Science}
    {University of Grenoble Alpes, France}
    {University of São Paulo, Brazil}
    {High-Performance Computing, Autotuning, Design of Experiments, Search
    Heuristics, Data Analysis}

    \workposition{2010 -- 2014} % Duration
    {BsC in Molecular Sciences}
    {}
    {University of São Paulo, Brazil}
    {Multiagent Systems, Digital Signal Processing}

\end{supertabular}

\switchcolumn % Switch to the next paracol column
\section{Selected Publications}
\label{sec:org348a3ec}
\longformpublication{\textbf{Bruel, P.}, Goldman, A., Chalamalasetti, S.R. and Milojicic, D., \textbf{2017}. \textit{Autotuning high-level synthesis for FPGAs using OpenTuner and LegUp}. In ReConFigurable Computing and FPGAs (ReConFig), 2017 International Conference on (pp. 1-6). IEEE.}

\longformpublication{\textbf{Bruel, P.}, Chalamalasetti, S.R., Dalton, C., El Hajj, I., Goldman, A., Graves, C., Hwu, W.M., Laplante, P., Milojicic, D., Ndu, G. and Strachan, J.P., \textbf{2017}. \textit{Generalize or Die: Operating Systems Support for Memristor-based Accelerators}. In 2017 IEEE International Conference on Rebooting Computing (ICRC) (pp. 1-8). IEEE.}

\longformpublication{\textbf{Bruel, P.}, Amarís, M. and Goldman, A., \textbf{2017}. \textit{Autotuning CUDA compiler parameters for heterogeneous applications using the OpenTuner framework}. Concurrency and Computation: Practice and Experience, 29(22), p.e3973.}

\longformpublication{\textbf{Bruel, P.}, Meirelles, P., Cobe, R., Goldman, A., \textbf{2017}. \textit{OpenMP or Pthreads: Which is Better for Beginners?}. In 8th Workshop on Evaluation and Usability of Programming Languages and Tools (PLATEAU).}

\longformpublication{Gonçalves, R., Amaris, M., Okada, T., \textbf{Bruel, P.} and Goldman, A., \textbf{2016}. \textit{Openmp is not as Easy as it Appears}. In System Sciences (HICSS), 2016 49th Hawaii International Conference on (pp. 5742-5751). IEEE.}

\longformpublication{\textbf{Bruel, P.} and Queiroz, M., \textbf{2014}. \textit{A Protocol for creating Multiagent Systems in Ensemble with Pure Data}. In International Computer Music Conference (ICMC).}

\medskip % Extra whitespace before the next section

%\end{paracol}
\section{Languages}
\label{sec:orgcd0d54e}
\begin{supertabular}{R{0.3\linewidth}R{0.3\linewidth}}
\tableentry{Portuguese}{Native}{}
\tableentry{English}{\textit{CEFR C2}}{}
\tableentry{French}{\textit{CEFR B2}}{}
\tableentry{Spanish}{\textit{CEFR A2}}{}
\end{supertabular}
\end{paracol}
%\switchcolumn % Switch to the next paracol column
\section{Skills}
\label{sec:org2a81626}
\begin{paracol}{1}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\begin{center}
\begin{supertabular}{C{0.3\linewidth}C{0.25\linewidth}C{0.3\linewidth}}
\tableheaderthree{Performance Tuning}{Software Engineering}{Tools and Infrastructure}{b}
\shrinkheight{3pt}
\tableentrythree{{\small\Ovalbox{Stochastic Search Heuristics}
                  \Ovalbox{Design of Experiments}
                  \Ovalbox{Optimal Experimental Design}
                  \Ovalbox{Performance Modeling}
                  \Ovalbox{Data Science}
                  }}
                 {{\small\Ovalbox{Python}
                   \Ovalbox{Julia}
                   \Ovalbox{R}
                   \Ovalbox{Bash}
                   \Ovalbox{C/C++}
                   \Ovalbox{OpenMP}
                   \Ovalbox{MPI}
                   \Ovalbox{CUDA C}
                   \Ovalbox{Java}
                   }}
                 {{\small\Ovalbox{GNU/Linux}
                   \Ovalbox{Git}
                   \Ovalbox{Grid5000}
                   \Ovalbox{GCE/AWS}
                   \Ovalbox{Automated Testing}
                   \Ovalbox{Continous Integration}
                   \Ovalbox{\LaTeX}
                   }}{}
\end{supertabular}
\end{center}
\end{paracol}
%\switchcolumn % Switch to the next paracol column
\end{document}
